### 2020-02-09 submission/methods.tex
Update methods.tex
Corrected a typo on line 92

\emph{The Weighted Alpha metric} is an average of $\hat{\alpha}$ over all layers, weighted by the size, or scale, or each matrix
(and approximates the average log $\alpha$-Norm metric).
\begin{equation}
\hat{\alpha} = \dfrac{1}{L}\sum_l \alpha_l\log\lambda_{max,l}\approx\langle\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}\rangle  
\end{equation}
where $L$ is the total nuumber of layer weight matrices.
The Weighted Alpha metric was introduced previously~\cite{MM20_SDM}, where it was shown to correlate well with trends in reported test accuracies of pretrained DNNs, albeit on a limited set of models.
Based on this, in this paper, we introduce and evaluate the $\alpha$-Norm metric.
One expects$\hat{\alpha}$ approximates the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

>>>>

\emph{The Weighted Alpha metric} is an average of $\hat{\alpha}$ over all layers, weighted by the size, or scale, or each matrix
(and approximates the average log $\alpha$-Norm metric).
\begin{equation}
\hat{\alpha} = \dfrac{1}{L}\sum_l \alpha_l\log\lambda_{max,l}\approx\langle\log\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}\rangle  
\end{equation}
where $L$ is the total nuumber of layer weight matrices.
The Weighted Alpha metric was introduced previously~\cite{MM20_SDM}, where it was shown to correlate well with trends in reported test accuracies of pretrained DNNs, albeit on a limited set of models.
Based on this, in this paper, we introduce and evaluate the $\alpha$-Norm metric.
One expects$\hat{\alpha}$ approximates the log $\alpha$-Norm very well for $\alpha < 2$ and reasonably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.
